# Setup
```{r setup, warning = F, message = F}
library(tidyverse) # General use & plotting etc
library(lubridate) # date functions
library(data.table) # for faster functions
library(scales) # for figures

knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_bw())
theme_update(
  axis.title = element_text(size = 12),
  strip.background = element_rect(fill = "white"),
  strip.text = element_text(size = 12),
  panel.grid = element_line(colour = "gray95"),
  legend.position = "none")

options(scipen = 999)

.libPaths("H:/DaSH477/Methods/R Libraries")
```

# Data
```{r data}
# from Will's prep
# load data and add a few columns
# this should be moved to the cleaning file
camhs_joined <- 
  fread("H:/DaSH477/Data/Cleaned Data/Jess/camhs_joined.csv", 
        sep = ",") %>%
  mutate(school_ages = case_when(
    age_at_referral >= 0  &  age_at_referral <= 4    ~ "Pre-Schoolers",
    age_at_referral >= 5  &  age_at_referral <= 7    ~ "Lower Primary",
    age_at_referral >= 8  &  age_at_referral <= 11   ~ "Upper Primary",
    age_at_referral >= 12 & age_at_referral  <= 14   ~ "Lower Secondary",
    age_at_referral >= 15 & age_at_referral  <= 18   ~ "Upper Secondary"),
        school_ages = ordered(school_ages, 
              levels = c("Pre-Schoolers", "Lower Primary", "Upper Primary", "Lower Secondary", "Upper Secondary", "School Leavers")),
         year = year(referred_date),
         half_year = floor_date(referred_date, "halfyear"),
         quarter = floor_date(referred_date, "quarter"),
         bimonth = floor_date(referred_date, "bimonth"),
         month_year = floor_date(referred_date, "month"),
         sex = if_else(sex == "U", NA_character_, as.character(sex)))

#create df that is one row per referral (remove rows for visits from one referral)
camhs_referrals <-
  camhs_joined %>%
  group_by(dash_uid, referred_date) %>%
  slice_head() %>% 
  ungroup()

#if they get an appointment say their referral was accepted
camhs_referrals <-
  camhs_referrals %>%
  mutate(rejected_referral = 
           ifelse(!is.na(appointment_date), 
                  2, 
                  rejected_referral))

#add referral count
camhs_referrals <-
  camhs_referrals %>%
  group_by(dash_uid) %>%
  arrange(referred_date) %>%
  mutate(referral_number = row_number()) %>%
  ungroup()


rm(camhs_joined)

#Grampian total population numbers (Will's)
population_data <- read_csv("cleaned_pop_simd_2012-2020.csv")

#Calculate mean population per SIMD decile
#for the years 2015 - 2020
population_by_simd <-
  population_data %>%
  filter(age %in% c(2:17)) %>%
  filter(year >= 2015) %>%
  group_by(year, decile) %>%
  summarise(pop = sum(count),
            .groups = "drop") %>%
  group_by(decile) %>%
  summarise(mean_pop = mean(pop))
```


#Cohort
```{r cohort}
#limit cohort date range, age, completeness
camhs_referrals <-
  camhs_referrals %>%
  filter(!is.na(sex)) %>%  # Small numbers
  filter(!is.na(year)) %>% # NA referred dates
  filter(age_at_referral <= 17) %>% #Small numbers
  filter(age_at_referral >= 2) %>% #Small numbers
  filter(year >= 2015) #trim to 5 years before COVID
```

# Age referrals
```{r refs by age}
referrals_by_age <-
camhs_referrals %>%
  group_by(age_at_referral) %>%
  summarise(referrals = n(),
            people = n_distinct(dash_uid)) %>%
  write_csv("referrals_by_age.csv")

#Figure 1
referrals_by_age %>%
  ggplot(aes(age_at_referral, referrals)) +
  geom_col() +
  labs(x = "Age", y = "Referrals (2015-2021)\n") +
  scale_x_continuous(breaks = c(2:17)) +
  scale_y_continuous(breaks = seq(from = 0, to = 3000, by = 500)) +
  theme(legend.position = "none")
```

# Age+sex referrals
```{r refs by age sex}
referrals_by_age_sex <-
camhs_referrals %>%
  group_by(age_at_referral, sex) %>%
  summarise(referrals = n(),
            people = n_distinct(dash_uid),
            .groups = "drop") %>%
  write_csv("referrals_by_age_sex.csv")

#Figure 2
referrals_by_age_sex %>%
  ggplot(aes(age_at_referral, referrals, fill = sex)) +
  geom_col(position = "dodge", width = 0.75) +
  facet_wrap(~sex) +
  labs(x = "Age", y = "Referrals (2015-2021)\n") +
  scale_x_continuous(breaks = c(2:17)) +
  theme(strip.text = element_blank())

#Figure 3
referrals_by_age_sex %>%
  ggplot(aes(age_at_referral, referrals, fill = sex)) +
  geom_col(position = "dodge") +
  labs(x = "Age", y = "Referrals (2015-2021)\n") +
  scale_x_continuous(breaks = c(2:17)) 
```

# SIMD referrals
```{r refs by simd}
referrals_by_simd <-
  camhs_referrals %>%
  group_by(simd2020_decile) %>%
  summarise(total_referrals = n(),
            people = n_distinct(dash_uid)) %>%
  left_join(., population_by_simd, 
            by = c("simd2020_decile" = "decile")) %>%
  mutate(refs_per_100 = total_referrals / mean_pop * 100) %>%
  write_csv("referrals_by_simd.csv")

#Figure 4
referrals_by_simd %>%
  ggplot(aes(simd2020_decile, refs_per_100)) +
  geom_point(size = 2, color = "darkgreen") +
  geom_line(size = 1, color = "darkgreen") +
  scale_x_reverse(breaks = c(1:10),
                     labels = 
                       c("most\ndeprived 10% of\nScotland", 
                         "","","","","","","","",
                         "least\ndeprived 10% of\nScotland")) +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30),
                     limits = c(0, NA)) +
  labs(x = "Deprivation level of home area", 
       y = "Referrals (2015-2021)\n per 100 children\n") 
```


# SIMD+age first referral
```{r refs by simd age}
first_referral_by_age_simd <-
camhs_referrals %>%
  filter(referral_number == 1) %>%
  group_by(simd2020_decile) %>%
  summarise(mean_age = mean(age_at_referral),
           .groups = "drop") %>%
  write_csv("referral_by_simd_age.csv")

#Figure 6
first_referral_by_age_simd %>%
  ggplot(aes(simd2020_decile, mean_age)) +
  geom_point(size = 2, color = "darkgreen") +
  geom_line(size = 1, color = "darkgreen") +
  ylim(c(8, 12)) +
  scale_x_reverse(breaks = c(1:10),
                     labels = 
                       c("most\ndeprived 10% of\nScotland", 
                         "","","","","","","","",
                         "least\ndeprived 10% of\nScotland")) +
  labs(x = "Deprivation level of home area",
       y = "Age at First Referral (mean)\n")
```

# Time referrals
```{r refs by quarter}
referrals_per_quarter <-
camhs_referrals %>%
  filter(month_year != ymd("2021-10-01")) %>% #remove due to quarters
  group_by(quarter) %>%
  summarise(total_referrals = n(),
            people = n_distinct(dash_uid)) %>%
  write_csv("referrals_by_quarter.csv")

referrals_per_quarter %>%
  ggplot(aes(quarter, total_referrals)) +
  geom_line(size = 1, color = "darkblue") +
  geom_point(size = 1.5, color = "darkblue") +
  ylim(0, NA) +
  labs(x = "", y = "Referrals per quarter\n") +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  theme(axis.text = element_text(size = 12),
        plot.margin = unit(c(0,0.5,0,0), unit = "cm"))
```

# Covid change
```{r refs covid change}
#mean referrals before March 2020
referrals_per_quarter %>%
  filter(quarter < ymd("2020-03-01")) %>%
  summarise(mean = mean(total_referrals))

#mean referrals from October 2020 
referrals_per_quarter %>%
  filter(quarter >= ymd("2020-10-01")) %>%
  summarise(mean = mean(total_referrals))

#rise in refs after first lockdown
(932-796)/796
```

#Time+school referrals
```{r refs by quarter school}
referral_by_quarter_school <-
  camhs_referrals %>%
  filter(referred_date < ymd("2021-10-01")) %>%
  group_by(quarter, school_ages) %>%
  summarise(total_referrals = n(),
            people = n_distinct(dash_uid),
            .groups = "drop") %>%
  write_csv("referrals_by_quarter_school.csv")

#Figure
referral_by_quarter_school %>%
  filter(school_ages == "Pre-Schoolers") %>%
  ggplot(aes(quarter, total_referrals)) +
  geom_point(alpha = 0.2, color = "red") +
  geom_smooth(
    se = F, size = 1.5, color = "red", span = 1) +
  ylim(0, NA) +
  facet_wrap(~school_ages, scales = "fixed", nrow = 1) +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  labs(x = "", y = "Referrals Per Quarter\n") 
```

#Time+school2 referrals
```{r refs by quarter school 2, fig.width=10, fig.height=4}
#Figure
referral_by_quarter_school %>%
  ggplot(aes(quarter, total_referrals, color = school_ages)) +
  geom_point(alpha = 0.2) +
  geom_smooth(se = F, size = 1.5, span = 1) +
  ylim(0, 400) +
  facet_wrap(~school_ages, scales = "fixed", nrow = 1) +
  scale_color_discrete() +
  labs(x = "", y = "Referrals Per Quarter\n") 
```


```{r refs by quarter school sex, fig.width=10, fig.height=4}
referral_by_halfyear_school_sex <-
  camhs_referrals %>%
  filter(referred_date < ymd("2021-07-01")) %>%
  group_by(half_year, school_ages, sex) %>%
  summarise(total_referrals = n(),
            people = n_distinct(dash_uid),
            .groups = "drop") %>%
  
  write_csv("referrals_by_halfyear_school_sex.csv")

referral_by_halfyear_school_sex %>%
  ggplot(aes(half_year, total_referrals, color = sex)) +
  geom_point(alpha = 0.2) +
  geom_smooth(se = F, size = 1.5, span = 2) +
  facet_wrap(~school_ages, scales = "fixed", nrow = 1) +
  scale_color_discrete() +
  labs(x = "", y = "Referrals Per 6-months\n")
```

#SIMD+time referrals
```{r, fig.width=8, fig.height=4}
population_data <-
  population_data %>%
  mutate(quintile = case_when(decile %in% c(1, 2) ~ 1,
                              decile %in% c(3, 4) ~ 2,
                              decile %in% c(5, 6) ~ 3,
                              decile %in% c(7, 8) ~ 4,
                              decile %in% c(9, 10) ~ 5)) 

pop_year_quintile <-
  population_data %>%
  group_by(year, quintile) %>%
  summarise(population = sum(count),
            .groups = "drop")

pop_year_quintile <-
bind_rows(pop_year_quintile,
          data_frame(
            year = c(2021, 2021, 2021, 2021, 2021),
            quintile = c(1:5),
            population = c(8938, 24089, 32380, 45932, 46943)
          ))

referrals_by_simd_year <-
camhs_referrals %>%
  group_by(year, simd2020_quintile) %>%
  summarise(referrals = n(),
            .groups = "drop") %>%
  left_join(., pop_year_quintile,
            by = c("year" = "year",
                   "simd2020_quintile" = "quintile")) %>%
  mutate(ref_rate_per_100 = referrals/population * 100) %>%
  write_csv("referrals_by_simd_year.csv")

labels <- 
  c("1" = "Most deprived 20%", "2" = "", "3" = "", "4" = "", "5" = "Least deprived 20%")

referrals_by_simd_year %>%
  filter(year <= 2020) %>%
  ggplot(aes(year, ref_rate_per_100, 
             group = simd2020_quintile, color = simd2020_quintile)) +
  geom_point(size = 2) +
  geom_line(size = 1.5, alpha = 0.5) +
  facet_wrap(~simd2020_quintile, ncol = 5,
             labeller = labeller(
               simd2020_quintile = labels)) +
  labs(y = "Referrals per 100 people\n") +
  theme(strip.text = element_text(size = 10)) +
  scale_x_continuous(breaks = c(2016, 2018, 2020)) +
  scale_y_continuous(limits = c(0, NA))
```

#Time rejections
```{r}
rejections_month <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>% #recent referrals na
  group_by(month_year) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals) %>%
  write_csv("rejections_by_month.csv")


#Figure
rejections_month %>%
  ggplot(aes(month_year, proportion_rejected)) +
  geom_point(alpha = 0.4, color = "darkred") +
  geom_smooth(se = F, size = 1.5, color = "darkred") +
  labs(x = "", y = "Referrals Rejected\n") +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  scale_y_continuous(labels = percent_format(accuracy = 5L), limits = c(0, 0.4)) 

#Table
camhs_referrals %>%
  filter(referred_date <= ymd("2021-06-01")) %>%
  group_by(year) %>%
  summarise(total_referrals = n(),
            referrals_month = total_referrals / 12, #fix 2021
            total_rejections = sum(rejected_referral == 1, na.rm = T),
            prop_rejected = total_rejections / total_referrals) 
```

# Time+sex rejections
```{r}
rejections_by_quarter_sex <-
  camhs_referrals %>%
  filter(quarter <= ymd("2021-06-01")) %>%
  group_by(quarter, sex) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals,
    .groups = "drop") %>%
  write_csv("rejections_by_quarter_sex.csv")


rejections_by_quarter_sex %>%
  ggplot(aes(quarter, proportion_rejected, color = sex)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se = F, size = 1.5) +
  labs(x = "", y = "Referrals Rejected\n") +
  theme(legend.position = "none") +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  scale_y_continuous(labels = percent_format(accuracy = 5L), limits = c(0, 0.5)) 
```

# Age+sex rejections
```{r, fig.width=6}
rejections_by_age_sex <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>% #recent referrals na 
  filter(age_at_referral > 2) %>% #smallish numbers
  group_by(sex, age_at_referral) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejectd = 
      n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals,
    .groups = "drop") %>%
  write_csv("rejections_by_age_sex.csv")

#Figure
rejections_by_age_sex %>%
  ggplot(aes(age_at_referral, proportion_rejected, fill = sex)) +
  geom_col(position = "dodge") +
  facet_wrap(~sex) +
  labs(x = "Age", y = "Referrals Rejected\n(2015-2021)\n") +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, 0.4)) +
  scale_x_continuous(breaks = c(3:17)) +
  theme(strip.text = element_blank())
```

```{r}
#Figure
rejections_by_age_sex %>%
  ggplot(aes(age_at_referral, proportion_rejected, fill = sex)) +
  geom_col(position = "dodge") +
  labs(x = "Age", y = "Referrals Rejected\n(2015-2021)\n") +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, 0.4)) +
  scale_x_continuous(breaks = c(3:17)) 
```

# SIMD rejections
```{r}
rejections_by_simd <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>% #recent referrals na
  group_by(simd2020_decile) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = 
      n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals) %>%
  write_csv("rejections_by_simd.csv")

#Figure
rejections_by_simd %>%
  ggplot(aes(simd2020_decile, proportion_rejected)) +
  geom_point(size = 2, color = "darkgreen") +
  geom_line(size = 1, color = "darkgreen") +
  labs(x = "Deprivation level of home area", y = "Referrals Rejected\n(2015-2021)\n") +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, .3)) +
  scale_x_reverse(breaks = c(1:10),
                     labels = 
                       c("most\ndeprived 10% of\nScotland", 
                         "","","","","","","","",
                         "least\ndeprived 10% of\nScotland")) 
```

# SIMD+time rejections
```{r, fig.width=8, fig.height=4}
rejections_by_simd_year <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>% #recent referrals na
  group_by(year, simd2020_quintile) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = 
      n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals) %>%
  write_csv("rejections_by_simd_year.csv")

rejections_by_simd_year %>%
  ggplot(aes(year, proportion_rejected, 
             group = simd2020_quintile, 
             color = simd2020_quintile)) +
  geom_point(size = 2) +
  geom_line(size = 1.5, alpha = 0.5) +
  facet_wrap(~simd2020_quintile, ncol = 5,
             labeller = labeller(
               simd2020_quintile = labels)) +
  labs(y = "Rejection rate\n") +
  theme(strip.text = element_text(size = 10)) +
  scale_x_continuous(breaks = c(2016, 2018, 2020)) +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, .4)) 
```



# Time+school rejections
```{r, fig.width=10, fig.height=4}
rejections_by_halfyear_school <-
  camhs_referrals %>%
  filter(referred_date <= ymd("2021-06-01")) %>%
  group_by(half_year, school_ages) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = 
      n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals,
    .groups = "drop") %>%
  write_csv("rejections_by_halfyear_school.csv")

rejections_by_halfyear_school %>%
  ggplot(aes(half_year, proportion_rejected, color = school_ages)) +
  geom_point(alpha = 0.4) +
  geom_smooth(se = F, size = 1.5,
              span = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, 0.75),
                     breaks = c(0, 0.25, 0.5, 0.75)) +
  facet_wrap(~school_ages, scales = "fixed", nrow = 1) +
  scale_color_discrete() +
  labs(x = "", y = "Referrals Rejected\n") 
```

#Time+school+sex rejections
```{r, fig.width=10, fig.height=4}
rejections_by_year_school_sex <-
  camhs_referrals %>%
  filter(referred_date < ymd("2021-07-01")) %>%
  group_by(year, school_ages, sex) %>%
  summarise(
    total_referrals = n(),
    total_rejected = sum(rejected_referral == 1, na.rm = T),
    people_rejected = 
      n_distinct(dash_uid[rejected_referral == 1]),
    proportion_rejected = total_rejected / total_referrals,
    .groups = "drop") %>%
  mutate(total_rejected = 
           ifelse(total_rejected < 5, NA, total_rejected),
         proportion_rejected = 
           ifelse(is.na(total_rejected), NA, proportion_rejected)) %>%
  write_csv("rejections_by_year_school_sex.csv")

#Figure
rejections_by_year_school_sex %>%
  ggplot(aes(year, proportion_rejected, color = sex)) +
  geom_point(alpha = 0.4, size = 2) +
  geom_smooth(se = F, size = 1.5, 
              span = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 5L), 
                     limits = c(0, NA),
                     breaks = c(0, 0.25, 0.5, 0.75)) +
  facet_wrap(~school_ages, scales = "fixed", nrow = 1) +
  scale_color_discrete() +
  labs(x = "", y = "Referrals Rejected\n") 
```

#Sex amplification
```{r}
girls_accepted_by_month_sex <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>%
  group_by(month_year) %>%
  summarise(
    referrals = n(),
    accepted_referrals = sum(
      rejected_referral == 2, na.rm = T),
    accepted_referrals_girl = sum(
      sex == "F" & rejected_referral == 2, na.rm = T),
    people_accepted_girls = 
      n_distinct(dash_uid[sex == "F" & rejected_referral == 2]),
    prop_accepted_referrals_girls =
      accepted_referrals_girl / accepted_referrals) %>%
  write_csv("girls_accepted_by_month_sex.csv")

girls_accepted_by_month_sex %>%
  ggplot(aes(month_year, prop_accepted_referrals_girls)) +
  geom_hline(yintercept = 0.5, color = "grey60") +
  geom_point(
    color = "#f8766d", size = 1.5, alpha = 0.3) +
  geom_smooth(size = 1.5, span = 1, se = F, color = "#f8766d") +
  labs(x = "", 
       y = "Accepted referrals\n that are GIRLS\n") +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  scale_y_continuous(
    labels = percent_format(accuracy = 5L), 
    limits = c(0.30, 0.70)) 
```

# Age amplification
```{r}
age_accepted_month <-
camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>%
  filter(rejected_referral == 2) %>%
  group_by(month_year) %>%
  summarise(mean_age = mean(age_at_referral)) %>%
  write_csv("age_accepted_by_month.csv")

age_accepted_month %>%
  ggplot(aes(month_year, mean_age)) +
  geom_point(alpha = 0.2, color = "darkgreen") +
  geom_smooth(
    se = F, size = 1.5, color = "#3d9954", span = 1) +
  scale_x_date(breaks = date_breaks("year"),
               labels = date_format("%Y")) +
  scale_y_continuous(limits = c(10, 13.5)) +
  labs(x = "", y = "Mean Age of\n Accepted Referrals\n") 
```

#SIMD steady
```{r}
simd_accepted_by_year <-
  camhs_referrals %>%
  filter(month_year <= ymd("2021-06-01")) %>%
  group_by(year, simd2020_quintile) %>%
  summarise(
    referrals = n(),
    accepted = 
      sum(rejected_referral == 2, na.rm = T),
    .groups = "drop") %>%
  left_join(., pop_year_quintile,
            by = c("year" = "year",
            "simd2020_quintile" = "quintile")) %>%
  mutate(accepted_rate = accepted / population * 100) %>%
  write_csv("simd_accepted_by_year.csv")

simd_accepted_by_year %>%
  filter(simd2020_quintile %in% c(1, 5),
         year <= 2020) %>%
  ggplot(aes(year, accepted_rate, group = as_factor(simd2020_quintile), color = as_factor(simd2020_quintile))) +
  geom_point(size = 1.5) +
  geom_line(size = 1.5, alpha = 0.5) +
  scale_y_continuous(limits = c(0, 2.5)) +
  scale_color_manual(
    labels = c("Most deprived", "Least deprived"),
    values = c("navyblue", "cornflowerblue")) +
  labs(y = "Accepted referrals\nper 100 people\n") +
  theme(legend.position = "right",
        legend.title = element_blank())
```


#Accepted Cohorts
```{r}
accepted_2016 <-
  camhs_referrals %>%
  filter(
    referred_date >= ymd("2015-06-01"),
    referred_date <= ymd("2016-05-31"),
    rejected_referral == 2) %>%
  group_by(dash_uid) %>%
  arrange(referred_date) %>%
  slice(1) %>%
  mutate(cohort = 2016)

accepted_2021 <-
  camhs_referrals %>%
  filter(
    referred_date >= ymd("2020-06-01"),
    referred_date <= ymd("2021-05-31"),
    rejected_referral == 2) %>%
  group_by(dash_uid) %>%
  arrange(referred_date) %>%
  slice(1) %>%
  mutate(cohort = 2021)

accepted <-
  bind_rows(accepted_2016, accepted_2021)

accepted %>%
  group_by(cohort) %>%
  summarise(people = n(),
            med_age = median(age_at_referral),
            iqr_age = IQR(age_at_referral),
            prop_boys = sum(sex == "M")/people,
            prop_deprived = sum(simd2020_quintile == 1)/people)
```











