---
title: "Grampian PIS"
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: spacelab
    orientation: columns
    vertical_layout: fill
    source_code: embed
runtime: shiny
resource_files:
- Data/Shapefile/NHSG_bivariate.shp
- Data/Shapefile/NHSG_bivariate.dbf
- Data/Shapefile/NHSG_bivariate.prj
- Data/Shapefile/NHSG_bivariate.shx
---

```{r global, include=FALSE}
options(scipen = 999)

library(flexdashboard)
library(shiny)
library(tidyverse)
library(janitor)
library(plotly)
library(paletteer)
library(cowplot)
library(lubridate)
library(rio)
library(sf)
library(biscale)
library(here)
library(ggpubr)
library(metR)

pis_data <- import_list(here("Data/PIS_dash_tables.xlsx"), setclass = "tbl")

mh_data <- import_list(here("Data/PIS_mh_tables.xlsx"), setclass = "tbl")

simd_pop <- import("Data/Population SIMD/cleaned_pop_simd_2012-2020.csv", delim = ",")

annual_totals <- import("Data/PIS_mh_annual.csv") %>% 
  rename(decile = "simd2020_decile")

pop_year <- simd_pop %>% 
  group_by(year) %>% 
  summarise(pop_estimate = sum(count))

dep_pop_annual <- simd_pop %>%
  group_by(year, decile) %>% 
  summarise(pop_estimate = sum(count))

dep_pop_avg <- dep_pop_annual %>% 
  group_by(decile) %>% 
  summarise(mean_pop = round(mean(pop_estimate)))

annual_individuals <- mh_data$`Annual Individuals by year` %>%
  filter(year <= 2020) %>%
  mutate(decile = simd2020_decile) %>% 
  group_by(year, decile) %>% 
  summarise(individuals = sum(n))

annual_totals <- annual_totals %>% 
  left_join(dep_pop_annual, by = c("decile", "year")) %>%
  left_join(annual_individuals, by = c("decile", "year")) %>% 
  mutate(rate = total / individuals,
         rate_per_k = (total / individuals)*1000,
         pop_rate = total / pop_estimate,
         pop_rate_per_k = (total / pop_estimate)*1000,
         proportion = (individuals / pop_estimate))

mean_totals <- annual_totals %>% 
  group_by(decile) %>% 
  summarise(mean_total = mean(total),
            mean_individuals = mean(individuals),
            mean_pop_estimate = mean(pop_estimate),
            mean_rate = mean_total/mean_individuals,
            mean_rate_upper = (1 / mean_individuals) * (mean_total + (1.96 * sqrt(mean_total))),
            mean_rate_lower = (1 / mean_individuals) * (mean_total - (1.96 * sqrt(mean_total))),
            mean_rate_per_hundred = mean_rate*100,
            mean_pop_rate = mean_total/mean_pop_estimate,
            mean_pop_rate_upper = (1 / mean_pop_estimate) * (mean_total + (1.96 * sqrt(mean_total))),
            mean_pop_rate_lower = (1 / mean_pop_estimate) * (mean_total - (1.96 * sqrt(mean_total))),
            mean_pop_rate_per_hundred = mean_pop_rate*100,
            mean_proportion = mean_individuals/mean_pop_estimate,
            mean_proportion_upper =
              mean_proportion + (1.96 * sqrt((mean_proportion * (1 - mean_proportion)) / mean_pop_estimate)),
            mean_proportion_lower =
              mean_proportion - (1.96 * sqrt((mean_proportion * (1 - mean_proportion)) / mean_pop_estimate)))

sf_nhsg <- read_sf(file.path("Data/Shapefile", "NHSG_bivariate.shp"))
```

Cohort Summary
=======================================================================

Sidebar {.sidebar data-width=300}
-----------------------------------------------------------------------

### **Community Dispensed Prescription Data**

This dashboard presents summarised prescription data related to the **NHS Grampian Children & Young People's Mental Health Cohort**.

The records include prescriptions for a selection of medications commonly used to treat Mental Health conditions which have been dispensed in the community between 2014-2021 for people who meet the following criteria:

- Live in NHS Grampian region
- Aged 0-24 at the time of prescription

***Note:*** Official Population Estimates have been used to calculate rates. These are available by year and SIMD Decile for all Scottish Health Board regions up to the year 2020.


Column {data-width=600}
-----------------------------------------------------------------------

### **Cohort Summary**    *(2021 Data only available up to May)*

```{r}
tab1 <- mh_data$`Cohort by Year` %>%
  left_join(pop_year, by = "year") %>% 
  mutate(year = format(round(year, 1)),
         per = format(round(per, 1)),
         per_pop = format(round(prescriptions/pop_estimate, 1)),
         prescriptions = format(round(prescriptions, 1), big.mark=","),
         individuals = format(round(individuals, 1), big.mark=","),
         pop_estimate = format(round(pop_estimate, 1), big.mark=","),
         prescriptions_per_month = format(round(prescriptions_per_month, 1), big.mark=",")) %>%
  select(year, prescriptions, individuals, per, pop_estimate, per_pop, prescriptions_per_month) %>% 
  rename(Year = year,
         Prescriptions = prescriptions,
         Individuals = individuals,
         'Individual Rate' = per,
         'Population Estimate' = pop_estimate,
         'Population Rate' = per_pop,
         'Prescriptions per month' = prescriptions_per_month)

renderTable(tab1, striped = TRUE, bordered = TRUE, align = "r")
```

### **Cohort Size Over Time** {data-height=600}

```{r}
plot1 <- mh_data$`Cohort by Year` %>%
  filter(!(year == "2021")) %>% 
  ggplot(aes(x = year, y = individuals)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  scale_y_continuous(name = "Individuals", limits = c(0,10500), breaks = seq(0, 10500, by = 1000), labels = scales::comma) +
  scale_x_continuous(name = "Year", breaks = seq(2012,2021, by = 1)) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(caption = "Source: NHS Grampian PIS") 

plot1 <- ggplotly(plot1)

renderPlotly(plot1)
```


Column {data-width=400}
-----------------------------------------------------------------------

### **Summary Statistics by Prescription**

```{r}
tab2 <- mh_data$`Summary by Prescription`

renderTable(tab2, na = "", striped = TRUE, bordered = TRUE, align = "r")
```


Total Prescriptions {data-orientation=rows}
=======================================================================

Sidebar {.sidebar data-width=350}
-----------------------------------------------------------------------

### **Top 20 Prescribed Items**

The tables here depict the most prescribed items for the total cohort 2014-2021, as well as broken down for males and females.

The numbers relate to instances of prescription, rather than people. That means that medications which are regularly prescribed to a small number of people may be higher in the list than medications prescribed to a large number of people only once or twice.

Row {.tabset data-height=600}
-----------------------------------------------------------------------

### **Most Prescribed Items - Total**

```{r}
tab5 <- mh_data$`Top Scripts` %>% 
  group_by(approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Prescriptions = n) %>% 
  mutate(Prescriptions = format(round(Prescriptions, 1), big.mark = ","))

tab5 <- tab5 %>% 
  left_join(mh_data$`Top Scripts`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "F") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Prescriptions, bnf_section_name) %>% 
  rename('BNF Section' = bnf_section_name)

renderTable(tab5, striped = TRUE, bordered = TRUE, align = "l")
```

### **Males**

```{r}
tab6 <- mh_data$`Top Scripts` %>% 
  group_by(chi_sex, approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  filter(chi_sex == "M") %>%
  select(!chi_sex) %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Prescriptions = n) %>% 
  mutate(Prescriptions = format(round(Prescriptions, 1), big.mark = ","))

tab6 <- tab6 %>% 
  left_join(mh_data$`Top Scripts`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "F") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Prescriptions, bnf_section_name) %>% 
  rename('BNF Section' = bnf_section_name)

renderTable(tab6, striped = TRUE, bordered = TRUE, align = "l")
```

### **Females**

```{r}
tab7 <- mh_data$`Top Scripts` %>% 
  group_by(chi_sex, approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  filter(chi_sex == "F") %>%
  select(!chi_sex) %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Prescriptions = n) %>% 
  mutate(Prescriptions = format(round(Prescriptions, 1), big.mark = ","))

tab7 <- tab7 %>% 
  left_join(mh_data$`Top Scripts`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "F") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Prescriptions, bnf_section_name) %>% 
  rename('BNF Section' = bnf_section_name)

renderTable(tab7, striped = TRUE, bordered = TRUE, align = "l")
```

Row {data-height=400}
-----------------------------------------------------------------------

### **Most Prescribed Items by Section**

```{r}
plot6 <- mh_data$`Top Section` %>%
  group_by(bnf_section_name) %>% 
  summarise(prescriptions = sum(n)) %>%
  mutate(bnf_section_name = fct_reorder(bnf_section_name, prescriptions)) %>% 
  ggplot(aes(x = bnf_section_name, y = prescriptions, fill = bnf_section_name)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  scale_y_continuous(limits = c(0,300000), breaks = seq(0, 300000, by = 50000), labels = scales::comma) +
  scale_fill_paletteer_d('rcartocolor::Bold') +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y = "Prescriptions",
       x = "",
       caption = "Source: NHS Grampian PIS") +
  coord_flip()

plot6 <- ggplotly(plot6)

renderPlotly(plot6)
```


Prescribed Individuals {data-orientation=rows}
=======================================================================

Sidebar {.sidebar data-width=350}
-----------------------------------------------------------------------

### **Top 20 Most Widely Prescribed Items**

The tables here depict the most widely prescribed items for the total cohort 2014-2021, as well as broken down for males and females.

The numbers relate to individuals who have received a prescription, rather than the total number of prescriptions. That means that an individuals could have been prescribed an item only once, or that they had many of the same prescription.

Row {.tabset data-height=600}
-----------------------------------------------------------------------

### **Most Prescribed Items - Total**

```{r}
tab8 <- mh_data$`Top Scripts Wide` %>% 
  group_by(approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Individuals = n) %>% 
  mutate(Individuals = format(round(Individuals, 1), big.mark = ","))

tab8 <- tab8 %>% 
  left_join(mh_data$`Top Scripts Wide`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "F") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Individuals, bnf_section_name) %>% 
  rename('BNF Chapter' = bnf_section_name)

renderTable(tab8, striped = TRUE, bordered = TRUE, align = "l")
```

### **Males**

```{r}
tab9 <- mh_data$`Top Scripts Wide` %>% 
  group_by(chi_sex, approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  filter(chi_sex == "M") %>%
  select(!chi_sex) %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Individuals = n) %>% 
  mutate(Individuals = format(round(Individuals, 1), big.mark = ","))

tab9 <- tab9 %>% 
  left_join(mh_data$`Top Scripts Wide`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "M") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Individuals, bnf_section_name) %>% 
  rename('BNF Chapter' = bnf_section_name)

renderTable(tab9, striped = TRUE, bordered = TRUE, align = "l")
```

### **Females**

```{r}
tab10 <- mh_data$`Top Scripts Wide` %>% 
  group_by(chi_sex, approved_name) %>% 
  summarise(n = sum(n)) %>%
  ungroup() %>% 
  filter(chi_sex == "F") %>%
  select(!chi_sex) %>% 
  arrange(desc(n)) %>% 
  top_n(20) %>% 
  mutate(rank = row_number()) %>% 
  select(rank, approved_name, n) %>% 
  rename(Rank = rank,
         Medication = approved_name,
         Individuals = n) %>% 
  mutate(Individuals = format(round(Individuals, 1), big.mark = ","))

tab10 <- tab10 %>% 
  left_join(mh_data$`Top Scripts Wide`, by = c("Medication" = "approved_name")) %>%
  filter(chi_sex == "F") %>% 
  group_by(Medication) %>% 
  top_n(1) %>% 
  select(Rank, Medication, Individuals, bnf_section_name) %>% 
  rename('BNF Chapter' = bnf_section_name)

renderTable(tab10, striped = TRUE, bordered = TRUE, align = "l")
```

Row {data-height=400}
-----------------------------------------------------------------------

### **Widest Prescribed Items - Females**

```{r}
plot7.1 <- mh_data$`Top Scripts Wide` %>%
  filter(chi_sex == "F") %>%
  arrange(desc(n), .by_group = T) %>%
  select(!bnf_section_name) %>% 
  top_n(10) %>%
  mutate(approved_name = fct_reorder(approved_name, n)) %>%
  ggplot(aes(x = approved_name, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  scale_y_continuous(limits = c(0,8000), breaks = seq(0, 8000, by = 500), labels = scales::comma, guide = guide_axis(angle = 65)) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(title = "Female",
       y = "Individuals",
       x = "",
       caption = "Source: NHS Grampian PIS") +
  coord_flip()

plot7.1 <- ggplotly(plot7.1)

renderPlotly(plot7.1)
```

### **Widest Prescribed Items - Males**

```{r}
plot7.2 <- mh_data$`Top Scripts Wide` %>%
  filter(chi_sex == "M") %>%
  arrange(desc(n), .by_group = T) %>%
  select(!bnf_section_name) %>% 
  top_n(10) %>%
  mutate(approved_name = fct_reorder(approved_name, n)) %>%
  ggplot(aes(x = approved_name, y = n)) +
  geom_bar(stat = "identity", fill = "springgreen4") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  scale_y_continuous(limits = c(0,8000), breaks = seq(0, 8000, by = 500), labels = scales::comma, guide = guide_axis(angle = 65)) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(title = "Male",
       y = "Individuals",
       x = "",
       caption = "Source: NHS Grampian PIS") +
  coord_flip()

plot7.2 <- ggplotly(plot7.2)

renderPlotly(plot7.2)
```


Deprivation {data-orientation=rows}
=======================================================================

Sidebar {.sidebar data-width=350}
-----------------------------------------------------------------------

### **Mental Health Prescription Rates in NHS Grampian have a Social Gradient by Deprivation**

The Scottish Index of Multiple Deprivation (SIMD) is a relative measure of material deprivation. It breaks Scotland into 6,976 small areas with roughly the same population and ranks them based on scores in 7 domains of deprivation: income, employment, education, health, access to services, crime and housing.

The SIMD is used by the Scottish Government and researchers to identify areas of multiple deprivation. Each area is ranked from 1 (Most Deprived) to 6,976 (Least Deprived). We've looked at these ranks in 10 groups, or deciles. Decile 1 includes areas which are in the most deprived 10% in Scotland.

This data is for people living in small areas in the NHS Grampian region only. Deprivation is not evenly spread in this region - There are relatively fewer people living in the most deprived areas, and relatively more living in the least deprived areas.

***Note:*** Deprivation is an area measure. Not every person living in a highly deprived area will experience a high level of deprivation themselves.


Row {data-height=500}
-----------------------------------------------------------------------

### **Prescriptions by Deprivation**

```{r}
tab3 <- mh_data$`MH prescriptions by dep` %>%
  left_join(dep_pop_avg, by = c("Deprivation" = "decile")) %>%
  # Calculate
  mutate('Population Rate' = format(round(Prescriptions/mean_pop, 1)),
         pop_prop_est = Individuals/mean_pop,
         prop_female = Females/Individuals) %>% 
  # Format
  mutate('Individual Rate' = format(round(individual_rate, 1)),
         Prescriptions = format(round(Prescriptions, 1), big.mark=","),
         Individuals = format(round(Individuals, 1), big.mark=","),
         'Population Estimate (Mean)' = format(round(mean_pop, 1), big.mark=","),
         Females = format(round(Females, 1), big.mark=","),
         '% Female' = scales::percent(prop_female, accuracy = 0.1),
         '% of Population Estimate' = scales::percent(pop_prop_est, accuracy = 0.1)) %>% 
  # Order
  select(Deprivation, Individuals, Prescriptions, 'Individual Rate', 'Population Estimate (Mean)', '% of Population Estimate', 'Population Rate', 'Median Age', 'IQR Age', Females, '% Female')

renderTable(tab3, striped = TRUE, bordered = TRUE, align = "r")
```

Row {data-height=500}
-----------------------------------------------------------------------

### **Prescription Rate for those with a Prescription**

```{r}
abs_range <- paste("Absolute Range:",
                   round(max(mean_totals$mean_rate) - min(mean_totals$mean_rate), digits = 2))
rel_range <- paste("Relative Range:",
                   round(max(mean_totals$mean_rate) / min(mean_totals$mean_rate), digits = 1))

plot2 <- mean_totals %>% 
  ggplot() +
  geom_point(aes(x = decile, y = mean_rate), size = 2, colour = "dark blue") +
  geom_smooth(method = "lm", aes(x = decile, y = mean_rate), se = FALSE, linetype = "dashed") +
  geom_errorbar(aes(x = decile, ymin = mean_rate_lower, ymax = mean_rate_upper), width = 0.2, alpha = .5) +
  scale_y_continuous(limits = c(0,1.4), breaks = seq(0,1.4,by=0.2)) + 
  scale_x_continuous(breaks = seq(1,10,by = 9),
                     labels = c("Most\nDeprived","Least\nDeprived")) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "",
       y = "") +
  ggtitle(paste0(abs_range,"\n",rel_range))

plot2 <- ggplotly(plot2)

renderPlotly(plot2)
```

### **Prescription Rate for total NHS Grampian Population**

```{r}
abs_range <- paste("Absolute Range:",
                   round(max(mean_totals$mean_pop_rate) - min(mean_totals$mean_pop_rate), digits = 1))
rel_range <- paste("Relative Range:",
                   round(max(mean_totals$mean_pop_rate) / min(mean_totals$mean_pop_rate), digits = 1))


plot3 <- mean_totals %>% 
  ggplot() +
  geom_point(aes(x = decile, y = mean_pop_rate), size = 2, colour = "dark red") +
  geom_smooth(method = "lm", aes(x = decile, y = mean_pop_rate), se = FALSE, linetype = "dashed") +
  geom_errorbar(aes(x = decile, ymin = mean_pop_rate_lower, ymax = mean_pop_rate_upper), width = 0.2, alpha = .5) +
  scale_y_continuous(limits = c(0,.7), breaks = seq(0,.7, by = 0.1)) + 
  scale_x_continuous(breaks = seq(1,10,by = 9),
                     labels = c("Most\nDeprived","Least\nDeprived")) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "",
       y = "") +
  ggtitle(paste0(abs_range,"\n",rel_range))

plot3 <- ggplotly(plot3)
  
renderPlotly(plot3)
```


Time Trends {data-orientation=rows}
=======================================================================

Sidebar {.sidebar data-width=350}
-----------------------------------------------------------------------

### **Medications 3: Mental Health Conditions**

These plots shows the monthly (top) and annual (bottom right) rates of prescriptions (per 1,000 population) for medications commonly used to treat mental health needs.

The bottom left plot also shows the total number of prescriptions for the whole period.

Row {data-height=500}
-----------------------------------------------------------------------

### **Monthly Rate of Mental Health Prescriptions 2014-2020**

```{r}
plot8 <- pis_data$`MH drugs` %>% 
  group_by(month_year, bnf_subsec_name) %>% 
  summarise(total = sum(n)) %>%
  ungroup() %>%
  mutate(year = year(month_year)) %>%  
  filter(!(year == "2021")) %>%
  left_join(pop_year, by = "year") %>%
  mutate(rate_per_k = (total/pop_estimate)*1000,
         month_year = lubridate::as_date(month_year)) %>%
  filter(!(bnf_subsec_name %in% c("Nicotine dependence", "Opioid dependence", "Drugs used for mania and hypomania", "Antipsychotic depot injections"))) %>% 
  ggplot() +
  geom_line(aes(x = month_year, y = rate_per_k, colour = fct_reorder(bnf_subsec_name, desc(rate_per_k))), size = 1) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
#  scale_y_continuous(limits = c(0,170), breaks = seq(0,160, by = 20)) +
  theme_classic() +
  scale_colour_paletteer_d('rcartocolor::Bold') +
  labs(x = "Year",
       y = "Prescriptions per 1,000 population") +
  theme(legend.title = element_blank())

plot8 <- ggplotly(plot8)

renderPlotly(plot8)
```

Row {data-height=500}
-----------------------------------------------------------------------

### **Total Mental Health Prescriptions 2014-2021**

```{r}
plot9 <- pis_data$`MH drugs` %>% 
  group_by(bnf_subsec_name) %>% 
  summarise(total = sum(n)) %>% 
  ungroup() %>%
  mutate(bnf_subsec_name = fct_reorder(bnf_subsec_name, desc(total))) %>% 
  filter(total >= 12000) %>%
  ggplot(aes(x = bnf_subsec_name, y = total, fill = bnf_subsec_name)) +
  geom_bar(stat = "identity") +
  scale_fill_paletteer_d('rcartocolor::Bold') +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  scale_y_continuous(limits = c(0,180000), breaks = seq(0,180000, by = 20000), labels = scales::comma,
                     guide = guide_axis(angle = 65)) +
  theme_classic() +
  labs(y = "Total Prescriptions",
       x = "",
       caption = "Source: NHS Grampian PIS") +
  coord_flip() +
  theme(legend.position = "none")

plot9 <- ggplotly(plot9)

renderPlotly(plot9)
```


### **Annual Rate of Mental Health Prescriptions 2014-2020**

```{r}
plot_ann <- pis_data$`MH drugs` %>% 
  group_by(year, bnf_subsec_name) %>% 
  summarise(total = sum(n)) %>%
  ungroup() %>% 
  filter(!(year == "2021")) %>%
  left_join(pop_year, by = "year") %>%
  mutate(rate_per_k = (total/pop_estimate)*1000) %>%
  filter(rate_per_k > 10) %>%
  filter(!(bnf_subsec_name == "Nicotine dependence")) %>% 
  ggplot() +
  geom_line(aes(x = year, y = rate_per_k, colour = fct_reorder(bnf_subsec_name, desc(rate_per_k))), size = 1) +
  scale_x_continuous(breaks = seq(2014,2020, by = 1)) +
  scale_y_continuous(limits = c(0,170), breaks = seq(0,160, by = 20)) +
  theme_classic() +
  scale_colour_paletteer_d('rcartocolor::Bold') +
  labs(x = "",
       y = "Prescriptions per 1,000 population") +
  theme(legend.title = element_blank(),
        legend.position = "none")

plot_ann <- ggplotly(plot_ann)

renderPlotly(plot_ann)
```

Maps {data-orientation=rows}
=======================================================================

Sidebar {.sidebar data-width=350}
-----------------------------------------------------------------------

### Geography

**Areas with higher Deprivation have higher proportions of their populations with a Mental Health prescription**

The Maps in the top panel show geographic patterns of deprivation and Mental Health prescriptions which takes into account differences in the size of populations within areas of deprivation.

***Light Grey*** areas are those with lower deprivation and lower proportions with a mental health prescription.

***Dark Blue*** areas are those with higher deprivation and higher proportions with a mental health prescription.

***Light Blue*** areas have intermediate deprivation and proportions with a mental health prescription.

The plots at the bottom show trends in this relationship over time.

Row {.tabset data-height=600}
-----------------------------------------------------------------------

### Aberdeen City

```{r}
pal <- "DkBlue"

map1 <- sf_nhsg %>% 
  filter(year == "2020") %>%
  filter(ca_name == "Aberdeen City") %>%
  ggplot() +
  geom_sf(mapping = aes(fill = bi_clss), color = "white", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = pal, dim = 3) +
  coord_sf(crs = st_crs(4326), datum = NA) +
  labs(caption = "Source: NHS Grampian PIS | NRS") +
  theme_void() +
  theme(plot.margin = unit(c(1,1,1,1), "cm"),
        plot.caption = element_text(size = 9, color = "grey50", hjust = 1, margin = margin(t = 15)))

map2 <- sf_nhsg %>% 
  filter(year == "2020") %>%
  filter(ca_name == "Aberdeenshire") %>% 
  ggplot() +
  geom_sf(mapping = aes(fill = bi_clss), color = "white", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = pal, dim = 3) +
  coord_sf(crs = st_crs(4326), datum = NA) +
    labs(caption = "Source: NHS Grampian PIS | NRS") +
  theme_void() +
  theme(plot.margin = unit(c(1,1,1,1), "cm"),
        plot.caption = element_text(size = 9, color = "grey50", hjust = 1, margin = margin(t = 15)))

map3 <- sf_nhsg %>% 
  filter(year == "2020") %>%
  filter(ca_name == "Moray") %>% 
  ggplot() +
  geom_sf(mapping = aes(fill = bi_clss), color = "white", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = pal, dim = 3) +
  coord_sf(crs = st_crs(4326), datum = NA) +
    labs(caption = "Source: NHS Grampian PIS | NRS") +
  theme_void() +
  theme(plot.margin = unit(c(1,1,1,1), "cm"),
        plot.caption = element_text(size = 9, color = "grey50", hjust = 1, margin = margin(t = 15)))

legend <- bi_legend(pal = pal, dim = 3, xlab = "Higher Relative Deprivation", ylab = "Higher % Population",  size = 10)

city <- ggdraw() +
  draw_plot(map1, 0,0,1,1) +
  draw_plot(legend, 0.1,0.4,0.3,0.3)

renderPlot(city)
```

### Aberdeenshire

```{r}
shire <- ggdraw() +
  draw_plot(map2, 0,0,1,1) +
  draw_plot(legend,0.1,0.4,.3,.3)

renderPlot(shire)
```

### Moray

```{r}
moray <- ggdraw() +
  draw_plot(map3, 0,0,1,1) +
  draw_plot(legend,0.1,0.4,.3,.3)

renderPlot(moray)
```

Row {.tabset data-height=400}
-----------------------------------------------------------------------

### Annual Proportions by Deprivation

```{r}
plot_city <- sf_nhsg %>% 
  ggplot() +
  geom_point(aes(x = smd_dcl, y = prop_pp), size = 2, colour = "dark red") +
  geom_smooth(method = "lm", aes(x = smd_dcl, y = prop_pp), se = FALSE, linetype = "dashed") +
  scale_y_continuous(limits = c(0,65)) +
  scale_x_continuous(breaks = seq(1,10,by=9),
                     labels = c("Most","Least")) +
  facet_wrap(~year, nrow = 1) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "Area Deprivation",
       y = "Proportion of Population w/ MH Prescription")

renderPlot(plot_city)
```



```{r}
### Annual Rates etc - NOT FOR DASHBOARD
library(lemon)

## Mean Individual Rates

abs_range <- paste("Absolute Range:",
                   round(max(mean_totals$mean_rate) - min(mean_totals$mean_rate), digits = 2))
rel_range <- paste("Relative Range:",
                   round(max(mean_totals$mean_rate) / min(mean_totals$mean_rate), digits = 1))

plot_rates <- mean_totals %>% 
  ggplot() +
  geom_errorbar(aes(x = decile, ymin = mean_rate_lower, ymax = mean_rate_upper), width = 0.2, alpha = .5) +
  geom_smooth(method = "lm", aes(x = decile, y = mean_rate), se = FALSE, linetype = "dashed") +
  geom_point(aes(x = decile, y = mean_rate), size = 2, colour = "dark blue") +
  scale_y_continuous(limits = c(0,1.4), breaks = seq(0,1.4,by=0.2)) + 
  scale_x_continuous(breaks = seq(1,10,by = 9),
                     labels = c("Most\nDeprived","Least\nDeprived")) +
#  facet_rep_wrap(~year, nrow = 3, repeat.tick.labels = "bottom") +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "",
       y = "") +
  ggtitle(paste0(abs_range,"\n",rel_range))
#  theme(panel.spacing.x = unit(4, "mm"),
#        axis.line = element_line())

## Mean Pop Rate
abs_range <- paste("Absolute Range:",
                   round(max(mean_totals$mean_pop_rate) - min(mean_totals$mean_pop_rate), digits = 1))
rel_range <- paste("Relative Range:",
                   round(max(mean_totals$mean_pop_rate) / min(mean_totals$mean_pop_rate), digits = 1))


plot_pop_rates <- mean_totals %>% 
  ggplot() +
  geom_errorbar(aes(x = decile, ymin = mean_pop_rate_lower, ymax = mean_pop_rate_upper), width = 0.2, alpha = .5) +
  geom_smooth(method = "lm", aes(x = decile, y = mean_pop_rate), se = FALSE, linetype = "dashed") +
  geom_point(aes(x = decile, y = mean_pop_rate), size = 2, colour = "dark red") +
  scale_y_continuous(limits = c(0,.7), breaks = seq(0,.7, by = 0.1)) + 
  scale_x_continuous(breaks = seq(1,10,by = 9),
                     labels = c("Most\nDeprived","Least\nDeprived")) +
#  facet_rep_wrap(~year, nrow = 3, repeat.tick.labels = "bottom") +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "",
       y = "") +
  ggtitle(paste0(abs_range,"\n",rel_range))


## Mean Proportions

abs_range <- paste("Absolute Range:",
                   round(max(mean_totals$mean_proportion)*100 - min(mean_totals$mean_proportion)*100, digits = 1))
rel_range <- paste("Relative Range:",
                   round(max(mean_totals$mean_proportion) / min(mean_totals$mean_proportion), digits = 1))

plot_mean_props <- mean_totals %>% 
  ggplot() +
  geom_errorbar(aes(x = decile, ymin = mean_proportion_lower, ymax = mean_proportion_upper), width = .2, alpha = .5) +
  geom_point(aes(x = decile, y = mean_proportion), size = 2, colour = "dark green") +
  geom_smooth(method = "lm", aes(x = decile, y = mean_proportion), se = FALSE, linetype = "dashed") +
  scale_y_continuous(limits = c(0,1), labels = scales::percent_format()) + 
  scale_x_continuous(breaks = seq(1,10,by = 9),
                     labels = c("Most\nDeprived","Least\nDeprived")) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  labs(x = "",
       y = "") +
  ggtitle(paste0(abs_range," Percentage Points","\n",rel_range))

plots <- plot_grid(plot_rates, plot_pop_rates, plot_mean_props, labels = NULL, nrow = 1, scale = 0.95)

ggsave("mean rates 2.png", plots, height = 5, width = 15, dpi = 500)

## Plotting Ranges

ranges <- annual_totals %>% 
  filter(decile == 1 | decile == 10) %>% 
  group_by(year) %>% 
  summarise(rate_abs = rate[decile == 1] - rate[decile == 10],
            rate_rel = rate[decile == 1] / rate[decile == 10],
            pop_rate_abs = pop_rate[decile == 1] - pop_rate[decile == 10],
            pop_rate_rel = pop_rate[decile == 1] / pop_rate[decile == 10],
            prop_abs = proportion[decile == 1] - proportion[decile == 10],
            prop_rel = proportion[decile == 1] / proportion[decile == 10])

compare <- annual_totals %>% 
  filter(decile == 1 | decile == 10) %>% 
  group_by(decile) %>% 
  summarise(mean_rate = mean(rate),
            mean_rate_per_k = mean(rate_per_k),
            mean_pop_rate = mean(pop_rate),
            mean_pop_per_k = mean(pop_rate_per_k))

lolli_plot <- compare %>% 
  ggplot() +
  geom_segment(aes(x = decile, xend = decile, y = mean_rate_per_k, yend = mean_pop_per_k), colour = "light grey") +
  geom_point(aes(x = decile, y = mean_rate_per_k), colour = "light blue", size = 3) +
  geom_point(aes(x = decile, y = mean_pop_per_k), colour = "red", size = 3) +
  scale_x_discrete(breaks = c(1,10), labels = c("1"="Most Deprived","10"="Least Deprived")) +
  coord_flip() +
  theme_classic() +
  theme(legend.position = "none")

### Monthly Totals
month_years <- tibble(month_year = seq(as_date("2014-01-01"), as_date("2021-05-01"), by = "month"))

plot_monthly <- pis_data$`MH drugs` %>% 
  group_by(month_year, bnf_section_name) %>% 
  summarise(total = sum(n)) %>%
  ungroup() %>%
  full_join(month_years, by = "month_year") %>% 
  mutate(year = year(month_year),
         month_year = lubridate::as_date(month_year)) %>% 
  ggplot() +
  geom_line(aes(x = month_year, y = total, colour = fct_reorder(bnf_section_name, desc(total))), size = 1) +
  geom_point(aes(x = month_year, y = total, colour = fct_reorder(bnf_section_name, desc(total))), size = 1) +
  geom_vline(xintercept = as.numeric(as_date("2020-03-26")), colour = "dark red", linetype = "dashed") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  scale_y_continuous(labels = scales::comma, breaks = seq(0,4000,by=500)) +
  theme_classic() +
  scale_colour_paletteer_d('rcartocolor::Bold', na.translate = F) +
  labs(x = "Year",
       y = "Prescriptions") +
  theme(legend.title = element_blank(),
        legend.background = element_rect(colour = NA, fill = NA),
        legend.position = c(.2,.85))

plot_monthly

ggsave("Pub/monthly_totals.png", height = 5.5, width = 9, plot_monthly, dpi = 500)
```

