---
title: "Inequalities"
author: "Will Ball"
date: "14/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
```

Code for calculating different index of inequality

## Libraries

```{r libraries, message = FALSE, warning = FALSE}
library(tidyverse)
library(here)
library(broom)
library(janitor)
library(data.table)
```

## Data

```{r data, message = FALSE, warning = FALSE}
# Population size by SIMD decile
simd_pop <- fread("Data/Population SIMD/cleaned_pop_simd_2012-2020.csv")

# Annual population by SIMD decile
dep_pop_annual <- simd_pop %>%
  group_by(year, decile) %>%
  summarise(pop_estimate = sum(count))

# Total annual prescriptions by SIMD decile
annual_totals <- fread("Data/PIS_mh_annual.csv") %>%
  rename(decile = "simd2020_decile")

# Rates of prescription by deprivation
dep_rates <- annual_totals %>%
  left_join(dep_pop_annual, by = c("decile", "year")) %>%
  mutate(pop_rate = total / pop_estimate) %>%
  group_by(year) %>%
  mutate(
    overall_rate = sum(total) / sum(pop_estimate),
    total_pop = sum(pop_estimate),
    proportion_pop = pop_estimate / total_pop,
    area = "NHS Grampian",
    per_hundred = pop_rate * 100,
    overall_per_hundred = overall_rate * 100
  )

# Mean Rates
mean_rates <- dep_rates %>%
  group_by(decile) %>%
  summarise(
    mean_total = round(mean(total)),
    mean_pop = round(mean(pop_estimate)),
    mean_pop_rate = mean_total / mean_pop
  ) %>%
  ungroup() %>%
  mutate(
    total_pop = sum(mean_pop),
    proportion_pop = mean_pop / total_pop,
    area = "NHS Grampian",
    overall_rate = sum(mean_total) / sum(mean_pop),
    per_hundred = mean_pop_rate * 100,
    overall_per_hundred = overall_rate * 100
  )
```

## Annual
## Slope of index on inequality (SII)

The calculations below are those of the linear SII, you will have to amend the model if you wanted to calculate the Poisson SII. This code will produce the results of the model, including confidence intervals

```{r chunk 1, message = FALSE, warning = FALSE}
sii_model <- dep_rates %>%
  group_by(area, year) %>%
  mutate(
    cumulative_pro = cumsum(proportion_pop), # cumulative proportion population for each area
    relative_rank = case_when(
      decile == 1 ~ 0.5 * proportion_pop,
      decile != 1 ~ lag(cumulative_pro) + 0.5 * proportion_pop
    ),
    sqr_proportion_pop = sqrt(proportion_pop), # square root of the proportion of the population in each SIMD
    relrank_sqr_proppop = relative_rank * sqr_proportion_pop,
    value_sqr_proppop = sqr_proportion_pop * per_hundred
  ) %>% # value based on population weights
  nest() %>% # creating one column called data with all the variables not in the grouping
  # Calculating linear regression for all the groups, then formatting the results
  # and calculating the confidence intervals
  mutate(
    model = map(data, ~ lm(value_sqr_proppop ~ sqr_proportion_pop + relrank_sqr_proppop + 0, data = .)),
    # extracting sii from model, a bit fiddly but it works
    sii = -1 * as.numeric(map(map(model, "coefficients"), "relrank_sqr_proppop")),
    cis = map(model, confint_tidy)
  ) %>% # calculating confidence intervals
  ungroup() %>%
  unnest(cis) %>% # Unnesting the CIs
  # selecting only even row numbers which are the ones that have the sii cis
  filter(row_number() %% 2 == 0) %>%
  mutate(
    lowci_sii = -1 * conf.high, # fixing interpretation
    upci_sii = -1 * conf.low
  ) %>%
  select(-conf.low, -conf.high) # non-needed variables

View(sii_model)

# Merging sii results with main data set
dep_rates <- left_join(dep_rates, sii_model, by = c("year", "area"))

View(dep_rates)
```

## Annual
## Relative index of inequality (RII)

This is the calculation of the linear RII which is based on the SII values, so that section needs to be run before this one.

```{r RII, message = FALSE, warning = FALSE}
dep_rates <- dep_rates %>%
  mutate(
    rii = sii / overall_per_hundred,
    lowci_rii = lowci_sii / overall_per_hundred,
    upci_rii = upci_sii / overall_per_hundred,
    # Transforming RII into %. This way is interpreted as "most deprived areas are
    # xx% above the average" For example: Cancer mortality rate is around 55% higher
    # in deprived areas relative to the mean rate in the population
    rii_int = rii * 0.5 * 100,
    lowci_rii_int = lowci_rii * 0.5 * 100,
    upci_rii_int = upci_rii * 0.5 * 100
  )

View(dep_rates)
```

## Mean
## Slope of index on inequality (SII)

The calculations below are those of the linear SII, you will have to amend the model if you wanted to calculate the Poisson SII. This code will produce the results of the model, including confidence intervals

```{r chunk 1, message = FALSE, warning = FALSE}
sii_model <- mean_rates %>%
  group_by(area) %>%
  mutate(
    cumulative_pro = cumsum(proportion_pop), # cumulative proportion population for each area
    relative_rank = case_when(
      decile == 1 ~ 0.5 * proportion_pop,
      decile != 1 ~ lag(cumulative_pro) + 0.5 * proportion_pop
    ),
    sqr_proportion_pop = sqrt(proportion_pop), # square root of the proportion of the population in each SIMD
    relrank_sqr_proppop = relative_rank * sqr_proportion_pop,
    value_sqr_proppop = sqr_proportion_pop * per_hundred
  ) %>% # value based on population weights
  nest() %>% # creating one column called data with all the variables not in the grouping
  # Calculating linear regression for all the groups, then formatting the results
  # and calculating the confidence intervals
  mutate(
    model = map(data, ~ lm(value_sqr_proppop ~ sqr_proportion_pop + relrank_sqr_proppop + 0, data = .)),
    # extracting sii from model, a bit fiddly but it works
    sii = -1 * as.numeric(map(map(model, "coefficients"), "relrank_sqr_proppop")),
    cis = map(model, confint_tidy)
  ) %>% # calculating confidence intervals
  ungroup() %>%
  unnest(cis) %>% # Unnesting the CIs
  # selecting only even row numbers which are the ones that have the sii cis
  filter(row_number() %% 2 == 0) %>%
  mutate(
    lowci_sii = -1 * conf.high, # fixing interpretation
    upci_sii = -1 * conf.low
  ) %>%
  select(-conf.low, -conf.high) # non-needed variables

View(sii_model)

# Merging sii results with main data set
mean_rates <- left_join(mean_rates, sii_model, by = "area")

View(mean_rates)
```

## Mean
## Relative index of inequality (RII)

This is the calculation of the linear RII which is based on the SII values, so that section needs to be run before this one.

```{r RII, message = FALSE, warning = FALSE}
mean_rates <- mean_rates %>%
  mutate(
    rii = sii / overall_per_hundred,
    lowci_rii = lowci_sii / overall_per_hundred,
    upci_rii = upci_sii / overall_per_hundred,
    # Transforming RII into %. This way is interpreted as "most deprived areas are
    # xx% above the average" For example: Cancer mortality rate is around 55% higher
    # in deprived areas relative to the mean rate in the population
    rii_int = rii * 0.5 * 100,
    lowci_rii_int = lowci_rii * 0.5 * 100,
    upci_rii_int = upci_rii * 0.5 * 100
  )

View(mean_rates)
```

## Plotting

```{r}
plot1 <- dep_rates %>% 
  ggplot(aes(x = year, y = sii)) +
  annotate("rect", ymin = 25.3, ymax = 41.3, xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "light blue") +
  geom_hline(yintercept = 33.2, alpha = 0.5, linetype = "dashed") +
  geom_pointrange(aes(ymin = lowci_sii, ymax = upci_sii), colour = "#012866", size = 0.5) +
  scale_x_continuous(breaks = seq(2012,2020,by=1)) +
  scale_y_continuous(limits = c(0,60), breaks = seq(0,60,by=10)) +
  labs(x = "Year", title = "Absolute Difference in Rate of Prescription per 100 people", y = "Slope Index of Inequality", caption = "Source: NHS Grampian PIS") +
  theme_classic() +
  theme(panel.grid.major.y = element_line())

plot1

ggsave(here("Pub","sii.png"), dpi = 500)

plot2 <- dep_rates %>% 
  ggplot(aes(x = year, y = rii_int)) +
  geom_pointrange(aes(ymin = lowci_rii_int, ymax = upci_rii_int), colour = "#012866", size = 0.5) +
  geom_hline(yintercept = 45, alpha = 0.5, linetype = "dashed") +
  annotate("rect", ymin = 34.3, ymax = 56, xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "light blue") +
  scale_x_continuous(breaks = seq(2012,2020,by=1)) +
  scale_y_continuous(limits = c(0,70), breaks = seq(0,70,by=10), labels = function(x) paste0("+", x, "%")) +
  labs(x = "Year", title = "Relative Difference in Rate of Prescription\nfor Most Deprived Areas Compared to Average", y = "Relative Index of Inequality", caption = "Source: NHS Grampian PIS") +
  theme_classic() +
  theme(panel.grid.major.y = element_line())

plot2

ggsave(here("Pub","rii.png"), dpi = 500)
```

